%-------------------------
% Resume in Latex
% Author: Anish Gondhi
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Anish Gondhi} \\ \vspace{1pt}
    \small (902)-718-9098 $|$ \href{mailto:Anish.Gondhi@dal.ca}{\underline{Anish.Gondhi@dal.ca}} $|$ 
    \href{https://www.linkedin.com/in/anish-gondhi/}{\underline{LinkedIn}} $|$
    \href{https://github.com/anishgondhi04}{\underline{GitHub}}
\end{center}


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL, HTML/CSS, JavaScript} \\
     \textbf{Frameworks}{: Spring Boot, JUnit, React} \\
     \textbf{Developer Tools}{: Git, GCC Compiler Tools, VS Code, PyCharm, IntelliJ, Android Studio, VIM, GitHub, GitLab} \\
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart


    \resumeSubheading
      {IT Analyst (IT Help Desk)}{Jan 2023 -- April 2023}
      {Dalhousie University}{Halifax, NS}
      \resumeItemListStart
        \resumeItem{Demonstrated excellent technical skills and knowledge in providing technical support to faculty members, staff, and students in the computer science department.}
        \resumeItem{Collaborated effectively with other technical support staff to troubleshoot and resolve complex technical issues and ensure seamless integration of systems.}
        \resumeItem{Conducted thorough testing and analysis of new software and hardware products.}
        \resumeItem{Developed and delivered comprehensive training sessions on various technical tools and systems.}
    \resumeItemListEnd

    \resumeSubheading
      {IT Solutions Developer }{Jan 2022 -- April 2022}
      {Emera Inc.}{Halifax, NS}
      \resumeItemListStart
        \resumeItem{Developed and tested Python scripts that helped users abstract data from API and push it into the company database. }
        \resumeItem{Implemented a time complexity algorithm to reduce the processing time of data transfer from the company API server to the SQL database.}
        \resumeItem{Re-crafted test cases for older products, resulting in an 85\% increase in test coverage and greater ease of comprehension.}
        \resumeItem{Integrated new data sources into Emera Energy’s data warehouse.}
        \resumeItem{Participated in daily standup meetings within an Agile development framework.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
       \resumeProjectHeading
          {\textbf{Quick Cash} $|$ \emph{Java, Android SDK, Firebase Realtime Database, Git, GitLab}}{Sept 2022 -- Dec 2022}
          \resumeItemListStart
            \resumeItem{Developed an Android application that functions as a job-board platform, designed to assist students in finding part-time and casual employment opportunities within their vicinity.}
            \resumeItem{Constructed the application from the ground up, incorporating geolocation features via the Google Maps API, a payment interface utilizing the PayPal API, and a recommendation engine to help employers identify suitable candidates based on their previous job experience.}
            \resumeItem{personally contributed to the project by integrating filter and search functionalities.}
            \resumeItem{Worked in a team of 6 developers and followed Agile Principles.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Music Player} $|$ \emph{JavaScript, ReactJS, Redux Toolkit, Tailwind CSS, Git, GitHub}}{Feb 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Resulted in an end product consisting of a front-end component of a music streaming service, which accessed data through APIs.}
            \resumeItem{Employed the Shazam API to retrieve artist and song data using the RapidAPI library and used Redux for state management.}
            \resumeItem{Implemented React Best practices for file structure and directory management.}
          \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{Trello Clone} $|$ \emph{Spring Boot, ReactJS, MariaDB, Git, GitHub}}{May 2022 -- Aug 2022}
          \resumeItemListStart
            \resumeItem{Developed a task-management web application clone using Spring Boot, ReactJS, and MariaDB.}
            \resumeItem{Used React to build the web application's front end.}
            \resumeItem{Created back-end using Sprint Boot with Models, Controllers, and Services.}
            \resumeItem{Implemented unit testing with the help of CI Pipeline.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dalhousie University}{Jan 2020 -- April 2024} 
      {Bachelor of Computer Science}{Halifax, NS}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
